### 2021-02-27 paper/base_model_specification.Rmd
Base model specification revisions

Our notation and assumptions closely follow that of Sadinle (2017). Denote two files as $\mathbf{X}_A$ and $\mathbf{X}_B$, with $n_A$ and $n_B$ records respectively, and with records indexed as $i \in \{1, \ldots, n_A\}$ in $\mathbf{X}_A$ and $j \in \{1, \ldots, n_B\}$ in $\mathbf{X}_B$. Without loss of generality, label the files such that $n_A \geq n_B$. We also assume there are no duplicates within files, only across. For each record pair under consideration, we generate a comparison vector $\boldsymbol{\gamma}_{ij} = \{\gamma_{ij}^1, \ldots, \gamma_{ij}^F\}$, where  $F$ is the number of fields used in the linkage and each takes $\gamma_{ij}^f$ takes on a value $l \in \{1, \ldots, L_f\}$ indicating level agreement between the two records on a specified field.

Following the Fellegi Sunter framework, we define $m^{fl}:= P(\gamma_{ij}^f = l |Z_j = i)$ to be the probability of observing agreement level $l$ in field $f$ for records $i$ and $j$ given that the records are a match, and similarly define $u^{fl}:= P(\gamma_{ij}^f = l |Z_j \neq i)$, for non-matches. We denote $\lambda$ to be the (marginal) probability that some record $j \in \mathbf{X}_B$ has a match in $\mathbf{X}_A$.

Lastly, we adopt from Sadinle 2017 the matching labelling $\mathbf{Z} = (Z_1, \ldots, Z_{n_A})$, defined as
$$Z_j=\begin{cases} 
    i,  & \text{if records } i\in \mathbf{X}_A \text{ and } j\in \mathbf{X}_B \text{ refer to the same entity}; \\
    n_A + 1,  & \text{if record } j\in \mathbf{X}_B \text{ does not have a match in file} \mathbf{X}_B; \\
\end{cases}$$

Wherever possible, we reserve superscripts for denoting field, level, and linkage cluster, and reserve subscripts for record indices. For example, $\mathbf{m}^f = (m^{f1}, \ldots, m^{fL_f})$ is the probability distribution governing field $f$ for matching records, and $\mathbf{m}_{ij}= \prod_{f=1}^{F}\prod_{l=1}^{L_f} \left(m^{fl}\right)^{\mathbf{1}_{\gamma_{ij}^f = l}} = P(\boldsymbol{\gamma}_{ij}|Z_j = i)$ is product of the relevant of the appropriate $\mathbf{m}$ parameters for record pair $(i,j)$. We hope that these conventions avoid overloaded notation in the likelihood and subsequent derivations.

@@

Additionally, our model differs from that of Sadinle 2017 through its explicit dependence on a beta random variable $\lambda$ that models the rate of matching across records. Sadinle marginalizes over such a random variable in his derivations of  the "beta prior for bipartite matching," but here we provide derivations without marginalizing in order to specify differing rates of matching for different linkage clusters.

@@

For fields $f \in \{1, \ldots, F\}$ and levels $l\in \{1, \ldots, L_f\}$ we adopt the following likelihood and prior distributions. Note that likelihood is related to that of Sadinle (2017), but includes dependence on the $\lambda$ random variable. It also makes it explict that units of observation under this model are the $n_B$ records in $\mathbf{X}_B$, a crucial distinction when compared to the likelihood over the $n_A \times n_B$ record pairs in the original Fellegi Sunter model.

@@

$$\lambda \sim \text{Beta}(\alpha_{\lambda}, \beta_{\lambda}) $$
The prior for $Z_j$ has equal probability of matching to all records $i\in \mathbf{X}_A$, and non-matching probability governed by $\lambda$. Therefore a  $\lambda \sim \text{Beta}(1, 1)$ corresponds to a prior belief that nonmatches and matches are equally likely, and a $\lambda \sim \text{Beta}(1, \frac{1}{n_A})$ prior corresponds to a uniform prior on the labelling of $\mathbf{Z}$.

@@

$$\mathbf{m^{f}}|\mathbf{Z}, \Gamma \sim \text{Dirichlet}(\alpha^{f1}(\mathbf{Z}), \ldots, \alpha^{fL_f}(\mathbf{Z}))$$
$$\mathbf{u^{f}}|\mathbf{Z}, \Gamma \sim \text{Dirichlet}(\beta^{f1}(\mathbf{Z}), \ldots, \beta^{fL_f}(\mathbf{Z}))$$
where $\alpha_{fl}(\mathbf{Z})= \sum_{i,j} I_{obs}(\gamma_{ij}^f)\mathbf{1}_{\gamma_{ij}^f = l} \mathbf{1}_{z_j = i}$ and $\beta_{fl}(\mathbf{Z})= \sum_{i,j} I_{obs}(\gamma_{ij}^f)\mathbf{1}_{\gamma_{ij}^f = l} \mathbf{1}_{z_j \neq i}$.

\underline{Sample $\lambda^{(s+1)}|\mathbf{Z}^{(s)}$ As a function of $\lambda$, the linkage structure parameter $\mathbf{Z}$ is sequence of successes (when $z_j < n_A + 1$) and failures (when $z_j = n_A + 1$), and therefore $p(\mathbf{Z}|\lambda) = \mathcal{L}(\lambda|\mathbf{Z})$ is  determined only by the number of dupliates $D = \sum_{i=1}^{n_B}\mathbf{1}_{z_j < n_A + 1}$ encoded by $\mathbf{Z}$. Thus we have

@@

\underline{Sample $\mathbf{Z}^{(s+1)}|\Gamma, \mathbf{m}^{(s+1)}, \mathbf{u}^{(s+1)}, \lambda^{(s+1)}$} Because we sample $Z_j$ independently of all other $Z_{j'}$, we use only the full conditional for an individual $Z_j$. Let $\Gamma_{.j}$ denote the set of $n_A$ comparison vectors with $j \in B$, and note that as a function of $Z_j$, the likelihood $p(\Gamma_{.j}|Z_j, \mathbf{m}, \mathbf{u})$ is a discrete distribution with probalities proportional to 
$$p(\Gamma_{.j}|Z_j = z_j, \mathbf{m}, \mathbf{u}) \propto \prod_{i=1}^{n_A}\mathbf{m}_{ij}^{\mathbf{1}_{z_j = i}}\mathbf{u}_{ij}^{\mathbf{1}_{z_j \neq i}}$$
$$\propto \prod_{i=1}^{n_A}\left(\frac{\mathbf{m}_{ij}}{\mathbf{u}_{ij}}\right)^{\mathbf{1}_{z_j = i}} \;\;\;\;\;\;\;\; \text{Divide through by} \prod_{i = 1}^{n_A}\mathbf{u}_{ij}$$
$$=
\begin{cases} 
    w_{ij}  & z_j \leq n_A; \\
    1 &  z_j  = n_A + 1 \\
\end{cases}$$

@@

Here, one should note that if we choose to integrate over the posterior of $\lambda$ and rearrange terms, we produce the following sampling mechanism:

>>>>

Our notation and assumptions closely follow that of Sadinle (2017). Denote two files as $A$ and $B$, with $n_A$ and $n_B$ records respectively, and with records indexed as $i \in \{1, \ldots, n_A\}$ in $A$ and $j \in \{1, \ldots, n_B\}$ in $B$. Without loss of generality, label the files such that $n_A \geq n_B$. We also assume there are no duplicates within files, only across. For each record pair under consideration, we generate a comparison vector $\boldsymbol{\gamma}_{ij} = \{\gamma_{ij}^1, \ldots, \gamma_{ij}^F\}$, where  $F$ is the number of fields used in the linkage and each $\gamma_{ij}^f$ takes on a value $l \in \{1, \ldots, L_f\}$ indicating level agreement between the two records on a specified field.

To indicate matching status, we adopt the *linkage structure parameter* $\mathbf{Z} = (Z_1, \ldots, Z_{n_A})$ from Sadinle 2017, defined as
$$Z_j=\begin{cases} 
    i,  & \text{if records } i\in A \text{ and } j\in B \text{ refer to the same entity}; \\
    n_A + 1,  & \text{if record } j\in B \text{ does not have a match in file } A; \\
\end{cases}$$
This provides more memory efficient storage for the linkage information than a $n_A \times n_B$ sparse matrix of indicators.

Following the Fellegi Sunter framework, we define $m^{fl}:= P(\gamma_{ij}^f = l |Z_j = i)$ to be the probability of observing agreement level $l$ in field $f$ for records $i$ and $j$ given that the records are a match, and similarly define $u^{fl}:= P(\gamma_{ij}^f = l |Z_j \neq i)$, for non-matches. We denote $\lambda$ to be the (marginal) probability that some record $j \in B$ has a match in $A$.

Wherever possible, we reserve superscripts for denoting field and level, while reserving subscripts for record indices. For example, $\mathbf{m}^f = (m^{f1}, \ldots, m^{fL_f})$ is the probability distribution governing field $f$ for matching records, and $\mathbf{m}_{ij}= \prod_{f=1}^{F}\prod_{l=1}^{L_f} \left(m^{fl}\right)^{\mathbf{1}_{\gamma_{ij}^f = l}} = P(\boldsymbol{\gamma}_{ij}|Z_j = i)$ is product of the relevant of the appropriate $\mathbf{m}$ parameters for record pair $(i,j)$. We hope that these conventions avoid overloaded notation in the likelihood and subsequent derivations.

@@

Our model differs from that of Sadinle 2017 through its explicit dependence on a beta random variable $\lambda$ that models the rate of matching across records. Sadinle marginalizes over such a random variable in his derivations of  the "beta prior for bipartite matching," but here we provide derivations without marginalizing in order to specify differing rates of matching for different linkage clusters.

@@

For fields $f \in \{1, \ldots, F\}$ and levels $l\in \{1, \ldots, L_f\}$ we adopt the following likelihood and prior distributions.

@@

$$\lambda \sim \text{Beta}(\alpha_{\lambda}, \beta_{\lambda}) $$
The prior for $Z_j$ has equal probability of matching to all records $i\in A$, and non-matching probability governed by $\lambda$. Therefore a  $\lambda \sim \text{Beta}(1, 1)$ corresponds to a prior belief that nonmatches and matches are equally likely, and a $\lambda \sim \text{Beta}(1, \frac{1}{n_A})$ prior corresponds to a uniform prior on the labelling of $\mathbf{Z}$.

@@

$$\mathbf{m}^f|\mathbf{Z}, \Gamma \sim \text{Dirichlet}(\alpha^{f1}(\mathbf{Z}), \ldots, \alpha^{fL_f}(\mathbf{Z}))$$
$$\mathbf{u}^f|\mathbf{Z}, \Gamma \sim \text{Dirichlet}(\beta^{f1}(\mathbf{Z}), \ldots, \beta^{fL_f}(\mathbf{Z}))$$
where $\alpha_{fl}(\mathbf{Z})= \sum_{i,j} I_{obs}(\gamma_{ij}^f)\mathbf{1}_{\gamma_{ij}^f = l} \mathbf{1}_{z_j = i}$ and $\beta_{fl}(\mathbf{Z})= \sum_{i,j} I_{obs}(\gamma_{ij}^f)\mathbf{1}_{\gamma_{ij}^f = l} \mathbf{1}_{z_j \neq i}$.

\underline{Sample $\lambda^{(s+1)}|\mathbf{Z}^{(s)}$} As a function of $\lambda$, the linkage structure parameter $\mathbf{Z}$ is sequence of successes (when $z_j < n_A + 1$) and failures (when $z_j = n_A + 1$), and therefore $p(\mathbf{Z}|\lambda) = \mathcal{L}(\lambda|\mathbf{Z})$ is  determined only by the number of dupliates $D = \sum_{i=1}^{n_B}\mathbf{1}_{z_j < n_A + 1}$ encoded by $\mathbf{Z}$. Thus we have

@@

\underline{Sample $\mathbf{Z}^{(s+1)}|\Gamma, \mathbf{m}^{(s+1)}, \mathbf{u}^{(s+1)}, \lambda^{(s+1)}$} Because we sample $Z_j$ independently of all other $Z_{j'}$, we use only the full conditional for an individual $Z_j$. Let $\Gamma_{.j}$ denote the set of $n_A$ comparison vectors with $j \in B$, and note that as a function of $Z_j$, the likelihood $p(\Gamma_{.j}|Z_j, \mathbf{m}, \mathbf{u}) = \mathcal{L}(Z_j|\Gamma_{.j}, \mathbf{m}, \mathbf{u})$ is a discrete distribution with probalities proportional to 
$$p(\Gamma_{.j}|Z_j = z_j, \mathbf{m}, \mathbf{u}) \propto \prod_{i=1}^{n_A}\mathbf{m}_{ij}^{\mathbf{1}_{z_j = i}}\mathbf{u}_{ij}^{\mathbf{1}_{z_j \neq i}}$$
$$\propto \prod_{i=1}^{n_A}\left(\frac{\mathbf{m}_{ij}}{\mathbf{u}_{ij}}\right)^{\mathbf{1}_{z_j = i}} \;\;\;\;\;\;\;\; \text{By dividing through by} \prod_{i = 1}^{n_A}\mathbf{u}_{ij}$$
$$=
\begin{cases} 
    w_{ij}  & z_j \leq n_A; \\
    1 &  z_j  = n_A + 1 \\
\end{cases}$$

@@

Here, we integrate over the posterior of $\lambda$ and rearrange terms to produce the final full conditional:

### 2021-02-27 paper/base_model_specification.tex
Base model specification revisions

Our notation and assumptions closely follow that of Sadinle (2017).
Denote two files as \(\mathbf{X}_A\) and \(\mathbf{X}_B\), with \(n_A\)
and \(n_B\) records respectively, and with records indexed as
\(i \in \{1, \ldots, n_A\}\) in \(\mathbf{X}_A\) and
\(j \in \{1, \ldots, n_B\}\) in \(\mathbf{X}_B\). Without loss of
generality, label the files such that \(n_A \geq n_B\). We also assume
there are no duplicates within files, only across. For each record pair
under consideration, we generate a comparison vector
\(\boldsymbol{\gamma}_{ij} = \{\gamma_{ij}^1, \ldots, \gamma_{ij}^F\}\),
where \(F\) is the number of fields used in the linkage and each takes
\(\gamma_{ij}^f\) takes on a value \(l \in \{1, \ldots, L_f\}\)
indicating level agreement between the two records on a specified field.

Following the Fellegi Sunter framework, we define
\(m^{fl}:= P(\gamma_{ij}^f = l |Z_j = i)\) to be the probability of
observing agreement level \(l\) in field \(f\) for records \(i\) and
\(j\) given that the records are a match, and similarly define
\(u^{fl}:= P(\gamma_{ij}^f = l |Z_j \neq i)\), for non-matches. We
denote \(\lambda\) to be the (marginal) probability that some record
\(j \in \mathbf{X}_B\) has a match in \(\mathbf{X}_A\).

Lastly, we adopt from Sadinle 2017 the matching labelling
\(\mathbf{Z} = (Z_1, \ldots, Z_{n_A})\), defined as \[Z_j=\begin{cases} 
    i,  & \text{if records } i\in \mathbf{X}_A \text{ and } j\in \mathbf{X}_B \text{ refer to the same entity}; \\
    n_A + 1,  & \text{if record } j\in \mathbf{X}_B \text{ does not have a match in file} \mathbf{X}_B; \\
\end{cases}\]

Wherever possible, we reserve superscripts for denoting field, level,
and linkage cluster, and reserve subscripts for record indices. For
example, \(\mathbf{m}^f = (m^{f1}, \ldots, m^{fL_f})\) is the
probability distribution governing field \(f\) for matching records, and
\(\mathbf{m}_{ij}= \prod_{f=1}^{F}\prod_{l=1}^{L_f} \left(m^{fl}\right)^{\mathbf{1}_{\gamma_{ij}^f = l}} = P(\boldsymbol{\gamma}_{ij}|Z_j = i)\)
is product of the relevant of the appropriate \(\mathbf{m}\) parameters
for record pair \((i,j)\). We hope that these conventions avoid
overloaded notation in the likelihood and subsequent derivations.

@@

Additionally, our model differs from that of Sadinle 2017 through its
explicit dependence on a beta random variable \(\lambda\) that models
the rate of matching across records. Sadinle marginalizes over such a
random variable in his derivations of the ``beta prior for bipartite
matching,'' but here we provide derivations without marginalizing in
order to specify differing rates of matching for different linkage
clusters.

@@

For fields \(f \in \{1, \ldots, F\}\) and levels
\(l\in \{1, \ldots, L_f\}\) we adopt the following likelihood and prior
distributions. Note that likelihood is related to that of Sadinle
(2017), but includes dependence on the \(\lambda\) random variable. It
also makes it explict that units of observation under this model are the
\(n_B\) records in \(\mathbf{X}_B\), a crucial distinction when compared
to the likelihood over the \(n_A \times n_B\) record pairs in the
original Fellegi Sunter model.

@@

\[\lambda \sim \text{Beta}(\alpha_{\lambda}, \beta_{\lambda}) \] The
prior for \(Z_j\) has equal probability of matching to all records
\(i\in \mathbf{X}_A\), and non-matching probability governed by
\(\lambda\). Therefore a \(\lambda \sim \text{Beta}(1, 1)\) corresponds
to a prior belief that nonmatches and matches are equally likely, and a
\(\lambda \sim \text{Beta}(1, \frac{1}{n_A})\) prior corresponds to a
uniform prior on the labelling of \(\mathbf{Z}\).

@@

\[\mathbf{m^{f}}|\mathbf{Z}, \Gamma \sim \text{Dirichlet}(\alpha^{f1}(\mathbf{Z}), \ldots, \alpha^{fL_f}(\mathbf{Z}))\]
\[\mathbf{u^{f}}|\mathbf{Z}, \Gamma \sim \text{Dirichlet}(\beta^{f1}(\mathbf{Z}), \ldots, \beta^{fL_f}(\mathbf{Z}))\]
where
\(\alpha_{fl}(\mathbf{Z})= \sum_{i,j} I_{obs}(\gamma_{ij}^f)\mathbf{1}_{\gamma_{ij}^f = l} \mathbf{1}_{z_j = i}\)
and
\(\beta_{fl}(\mathbf{Z})= \sum_{i,j} I_{obs}(\gamma_{ij}^f)\mathbf{1}_{\gamma_{ij}^f = l} \mathbf{1}_{z_j \neq i}\).

\textbackslash underline\{Sample \(\lambda^{(s+1)}|\mathbf{Z}^{(s)}\) As
a function of \(\lambda\), the linkage structure parameter
\(\mathbf{Z}\) is sequence of successes (when \(z_j < n_A + 1\)) and
failures (when \(z_j = n_A + 1\)), and therefore
\(p(\mathbf{Z}|\lambda) = \mathcal{L}(\lambda|\mathbf{Z})\) is
determined only by the number of dupliates
\(D = \sum_{i=1}^{n_B}\mathbf{1}_{z_j < n_A + 1}\) encoded by
\(\mathbf{Z}\). Thus we have

@@

\underline{Sample $\mathbf{Z}^{(s+1)}|\Gamma, \mathbf{m}^{(s+1)}, \mathbf{u}^{(s+1)}, \lambda^{(s+1)}$}
Because we sample \(Z_j\) independently of all other \(Z_{j'}\), we use
only the full conditional for an individual \(Z_j\). Let \(\Gamma_{.j}\)
denote the set of \(n_A\) comparison vectors with \(j \in B\), and note
that as a function of \(Z_j\), the likelihood
\(p(\Gamma_{.j}|Z_j, \mathbf{m}, \mathbf{u})\) is a discrete
distribution with probalities proportional to
\[p(\Gamma_{.j}|Z_j = z_j, \mathbf{m}, \mathbf{u}) \propto \prod_{i=1}^{n_A}\mathbf{m}_{ij}^{\mathbf{1}_{z_j = i}}\mathbf{u}_{ij}^{\mathbf{1}_{z_j \neq i}}\]
\[\propto \prod_{i=1}^{n_A}\left(\frac{\mathbf{m}_{ij}}{\mathbf{u}_{ij}}\right)^{\mathbf{1}_{z_j = i}} \;\;\;\;\;\;\;\; \text{Divide through by} \prod_{i = 1}^{n_A}\mathbf{u}_{ij}\]
\[=
\begin{cases} 
    w_{ij}  & z_j \leq n_A; \\
    1 &  z_j  = n_A + 1 \\
\end{cases}\]

@@

Here, one should note that if we choose to integrate over the posterior
of \(\lambda\) and rearrange terms, we produce the following sampling
mechanism:

>>>>

Our notation and assumptions closely follow that of Sadinle (2017).
Denote two files as \(A\) and \(B\), with \(n_A\) and \(n_B\) records
respectively, and with records indexed as \(i \in \{1, \ldots, n_A\}\)
in \(A\) and \(j \in \{1, \ldots, n_B\}\) in \(B\). Without loss of
generality, label the files such that \(n_A \geq n_B\). We also assume
there are no duplicates within files, only across. For each record pair
under consideration, we generate a comparison vector
\(\boldsymbol{\gamma}_{ij} = \{\gamma_{ij}^1, \ldots, \gamma_{ij}^F\}\),
where \(F\) is the number of fields used in the linkage and each
\(\gamma_{ij}^f\) takes on a value \(l \in \{1, \ldots, L_f\}\)
indicating level agreement between the two records on a specified field.

To indicate matching status, we adopt the \emph{linkage structure
parameter} \(\mathbf{Z} = (Z_1, \ldots, Z_{n_A})\) from Sadinle 2017,
defined as \[Z_j=\begin{cases} 
    i,  & \text{if records } i\in A \text{ and } j\in B \text{ refer to the same entity}; \\
    n_A + 1,  & \text{if record } j\in B \text{ does not have a match in file } A; \\
\end{cases}\] This provides more memory efficient storage for the
linkage information than a \(n_A \times n_B\) sparse matrix of
indicators.

Following the Fellegi Sunter framework, we define
\(m^{fl}:= P(\gamma_{ij}^f = l |Z_j = i)\) to be the probability of
observing agreement level \(l\) in field \(f\) for records \(i\) and
\(j\) given that the records are a match, and similarly define
\(u^{fl}:= P(\gamma_{ij}^f = l |Z_j \neq i)\), for non-matches. We
denote \(\lambda\) to be the (marginal) probability that some record
\(j \in B\) has a match in \(A\).

Wherever possible, we reserve superscripts for denoting field and level,
while reserving subscripts for record indices. For example,
\(\mathbf{m}^f = (m^{f1}, \ldots, m^{fL_f})\) is the probability
distribution governing field \(f\) for matching records, and
\(\mathbf{m}_{ij}= \prod_{f=1}^{F}\prod_{l=1}^{L_f} \left(m^{fl}\right)^{\mathbf{1}_{\gamma_{ij}^f = l}} = P(\boldsymbol{\gamma}_{ij}|Z_j = i)\)
is product of the relevant of the appropriate \(\mathbf{m}\) parameters
for record pair \((i,j)\). We hope that these conventions avoid
overloaded notation in the likelihood and subsequent derivations.

@@

Our model differs from that of Sadinle 2017 through its explicit
dependence on a beta random variable \(\lambda\) that models the rate of
matching across records. Sadinle marginalizes over such a random
variable in his derivations of the ``beta prior for bipartite
matching,'' but here we provide derivations without marginalizing in
order to specify differing rates of matching for different linkage
clusters.

@@

For fields \(f \in \{1, \ldots, F\}\) and levels
\(l\in \{1, \ldots, L_f\}\) we adopt the following likelihood and prior
distributions.

@@

\[\lambda \sim \text{Beta}(\alpha_{\lambda}, \beta_{\lambda}) \] The
prior for \(Z_j\) has equal probability of matching to all records
\(i\in A\), and non-matching probability governed by \(\lambda\).
Therefore a \(\lambda \sim \text{Beta}(1, 1)\) corresponds to a prior
belief that nonmatches and matches are equally likely, and a
\(\lambda \sim \text{Beta}(1, \frac{1}{n_A})\) prior corresponds to a
uniform prior on the labelling of \(\mathbf{Z}\).

@@

\[\mathbf{m}^f|\mathbf{Z}, \Gamma \sim \text{Dirichlet}(\alpha^{f1}(\mathbf{Z}), \ldots, \alpha^{fL_f}(\mathbf{Z}))\]
\[\mathbf{u}^f|\mathbf{Z}, \Gamma \sim \text{Dirichlet}(\beta^{f1}(\mathbf{Z}), \ldots, \beta^{fL_f}(\mathbf{Z}))\]
where
\(\alpha_{fl}(\mathbf{Z})= \sum_{i,j} I_{obs}(\gamma_{ij}^f)\mathbf{1}_{\gamma_{ij}^f = l} \mathbf{1}_{z_j = i}\)
and
\(\beta_{fl}(\mathbf{Z})= \sum_{i,j} I_{obs}(\gamma_{ij}^f)\mathbf{1}_{\gamma_{ij}^f = l} \mathbf{1}_{z_j \neq i}\).

\underline{Sample $\lambda^{(s+1)}|\mathbf{Z}^{(s)}$} As a function of
\(\lambda\), the linkage structure parameter \(\mathbf{Z}\) is sequence
of successes (when \(z_j < n_A + 1\)) and failures (when
\(z_j = n_A + 1\)), and therefore
\(p(\mathbf{Z}|\lambda) = \mathcal{L}(\lambda|\mathbf{Z})\) is
determined only by the number of dupliates
\(D = \sum_{i=1}^{n_B}\mathbf{1}_{z_j < n_A + 1}\) encoded by
\(\mathbf{Z}\). Thus we have

@@

\underline{Sample $\mathbf{Z}^{(s+1)}|\Gamma, \mathbf{m}^{(s+1)}, \mathbf{u}^{(s+1)}, \lambda^{(s+1)}$}
Because we sample \(Z_j\) independently of all other \(Z_{j'}\), we use
only the full conditional for an individual \(Z_j\). Let \(\Gamma_{.j}\)
denote the set of \(n_A\) comparison vectors with \(j \in B\), and note
that as a function of \(Z_j\), the likelihood
\(p(\Gamma_{.j}|Z_j, \mathbf{m}, \mathbf{u}) = \mathcal{L}(Z_j|\Gamma_{.j}, \mathbf{m}, \mathbf{u})\)
is a discrete distribution with probalities proportional to
\[p(\Gamma_{.j}|Z_j = z_j, \mathbf{m}, \mathbf{u}) \propto \prod_{i=1}^{n_A}\mathbf{m}_{ij}^{\mathbf{1}_{z_j = i}}\mathbf{u}_{ij}^{\mathbf{1}_{z_j \neq i}}\]
\[\propto \prod_{i=1}^{n_A}\left(\frac{\mathbf{m}_{ij}}{\mathbf{u}_{ij}}\right)^{\mathbf{1}_{z_j = i}} \;\;\;\;\;\;\;\; \text{By dividing through by} \prod_{i = 1}^{n_A}\mathbf{u}_{ij}\]
\[=
\begin{cases} 
    w_{ij}  & z_j \leq n_A; \\
    1 &  z_j  = n_A + 1 \\
\end{cases}\]

@@

Here, we integrate over the posterior of \(\lambda\) and rearrange terms
to produce the final full conditional:
